\prefacesection{Acknowledgements}

First and foremost, I would like to express my sincere gratitude to my advisor, Professor Lei Xing, for his guidance, support, and encouragement. He was one of the best researchers in the world in radiation oncology, and I was very fortunate and lucky to have had the opportunity to be his student. He dedicated a lot of time to all of his students. His office was always open to us, and he was always welcoming with whatever question we had. He was not only a truly outstanding researcher but also one who bestowed his knowledge upon us, even through osmosis. Just by being with him and seeing how patient and how he took his time on research problems inspired me. Almost every interaction with my advisor was a great learning experience, be it a lesson in critical thinking, problem solving, or persistence. I also want to thank him for giving me the independence to grow and mature both intellectually and psychologically. I thank him for being patient for many years with an immature kid who lacked the emotional maturity and nurturing me, providing me with insights and wisdoms that cannot be learned from books or anywhere else.

I would like to thank other members of my committee...... Professor Daniel Spielman was so encouraging. One of the first sentences he said was, "congratulations on making it this far." This was so encouraging to me. 

I also would like to thank both of my parents. First, I want to thank my dad. To me, he is one of the smartest man alive and in my heart, always a hero. My family came to the U.S. over 19 years ago to seek a better live and better opportunities and perhaps a bit cliche, to pursue the American dream. They took a lot of effort to get here. My parents did not come through the graduate school route, but rather through hard work. Every sweat and piece of suffering meant something for me. To me, a lot of people are losers in this world, but my dad is certainly not one - he is a winner in life. I also want to thank my mom, who was always there for me and took the time to make such a great family. She took a lot of energy and work to set up such a loving and caring family. Some people may not appreciate this, but it actually does take a lot of time and effort, and oftentimes, require a lot of sacrifices, to be a great housewife and raise a kid with both spouse's income summed close to minimum wages at the time. My mom did a lot for the family, at times even sacrificing some of her own dreams, to ensure that we had a stable family and loving environment that we can always come home to.

Lastly, I want to thank my friends. I thank to those who opened up to me and said what was on their mind. I appreciate the honesty. Our hearts connected through deep conversations. (At times, using our ability to think deeply, which we gained in our graduate training, to other areas of our lives was fun and rewarding) I'm glad I was able to be at such a unique place like Stanford where I could meet so many unique people who are so interesting. A high school teacher of mine once said it is not where you go but who you go with. It is so true that Stanford is such a great environment because of the number of talented people here, with whom I was so lucky to have the chance to interact with and learn from. Learning from talented people and people who think differently is truly a rewarding experience. I thank the Stanford Electrical Engineering department for giving me the opportunity to be here, to really open my eyes, and to see what excellence really means.